---
title: "🌦️ The Market Weather Report"
subtitle: "A plain-English forecast for the world's stock markets — plus a Sector & Theme Radar"
date: today
format:
  html:
    theme:
      - cosmo
      - weather-pastel.scss
    toc: true
    toc-location: left
    toc-depth: 3
    toc-expand: 2
    code-fold: true
    code-tools: true
    code-summary: "🧮 Peek at the quant machinery"
    embed-resources: true
    number-sections: true
    fig-width: 10
    fig-height: 5
    df-print: paged
    mainfont: "Nunito"
execute:
  warning: false
  message: false
  echo: true
knitr:
  opts_chunk:
    comment: "#>"
---

```{r setup}
#| include: false

## ---- Package bootstrap: install if missing, then load quietly ----------
need <- c("quantmod","TTR","xts","zoo","plotly","DT","forecast",
          "rvest","httr","jsonlite","dplyr","tidyr","htmltools","tibble")
for (p in need) {
  if (!requireNamespace(p, quietly = TRUE)) {
    try(install.packages(p, repos = "https://cloud.r-project.org"), silent = TRUE)
  }
}
suppressPackageStartupMessages({
  library(quantmod); library(TTR); library(xts); library(zoo)
  library(plotly);  library(DT);  library(forecast)
  library(rvest);   library(httr); library(jsonlite)
  library(dplyr);   library(tidyr); library(htmltools); library(tibble)
})

options(stringsAsFactors = FALSE)
set.seed(42)
LOOKBACK_YEARS <- 5.6    # buffer beyond 5y so the 5-year horizon always resolves
FROM_DATE <- Sys.Date() - round(365.25 * LOOKBACK_YEARS)

## ---- 🌊 Seafoam & Sky pastel palette (single source of truth) -----------
## Every chart, gauge and box below pulls from these tokens so the whole
## report reads like one friendly picture book — while the maths beneath
## stays fully grown-up.
PAL <- list(
  seafoam      = "#a8e6cf",  seafoam_deep = "#56c5a8",
  sky          = "#b3e5fc",  sky_deep     = "#81cfe8",
  butter       = "#fff3b0",  butter_deep  = "#ffe07a",
  peach        = "#ffd3b6",
  coral        = "#ffaaa5",  coral_deep   = "#f4837d",
  lavender     = "#e4d9ff",
  ink          = "#2f4858",  teal_ink     = "#00695c",
  cloud        = "#f2fbf8",  cloud_blue   = "#eef8fd",
  up           = "#3aa88a",  # readable pastel-compatible green for text
  down         = "#e57368"   # readable pastel-compatible red for text
)
## Shared plotly cosmetics: soft background, friendly font
pastel_layout <- function(p, ...) {
  plotly::layout(p, ...,
    paper_bgcolor = "#ffffff", plot_bgcolor = PAL$cloud_blue,
    font = list(family = "Nunito, Segoe UI, sans-serif", color = PAL$ink))
}
## Diverging ramp for heatmaps: coral → cloud → seafoam
pastel_diverge <- colorRamp(c(PAL$coral_deep, "#ffffff", PAL$seafoam_deep))
```

```{r universe}
#| include: false

## ---- The index universe, with a symbol map per data source -------------
indices <- tibble::tribble(
  ~name,               ~yahoo,        ~stooq,     ~proxy,        ~region,
  "S&P 500",           "^GSPC",       "^spx",     "SPY",         "North America",
  "Nasdaq Composite",  "^IXIC",       "^ndq",     "ONEQ",        "North America",
  "Dow Jones",         "^DJI",        "^dji",     "DIA",         "North America",
  "Russell 2000",      "^RUT",        "^rut",     "IWM",         "North America",
  "TSX Composite",     "^GSPTSE",     "^tsx",     "EWC",         "North America",
  "FTSE 100",          "^FTSE",       "^ukx",     "EWU",         "Europe",
  "DAX",               "^GDAXI",      "^dax",     "EWG",         "Europe",
  "CAC 40",            "^FCHI",       "^cac",     "EWQ",         "Europe",
  "Euro Stoxx 50",     "^STOXX50E",   "^stx50",   "FEZ",         "Europe",
  "IBEX 35",           "^IBEX",       "^ibex",    "EWP",         "Europe",
  "FTSE MIB",          "FTSEMIB.MI",  "^mib",     "EWI",         "Europe",
  "SMI (Swiss)",       "^SSMI",       "^smi",     "EWL",         "Europe",
  "Nikkei 225",        "^N225",       "^nkx",     "EWJ",         "Asia-Pacific",
  "TOPIX",             "1475.T",      "^tpx",     "EWJ",         "Asia-Pacific",
  "Hang Seng",         "^HSI",        "^hsi",     "EWH",         "Asia-Pacific",
  "Shanghai Comp.",    "000001.SS",   "^shc",     "ASHR",        "Asia-Pacific",
  "KOSPI",             "^KS11",       "^kospi",   "EWY",         "Asia-Pacific",
  "ASX 200",           "^AXJO",       "^axjo",    "EWA",         "Asia-Pacific",
  "Sensex",            "^BSESN",      "^snx",     "INDA",        "Asia-Pacific",
  "Nifty 50",          "^NSEI",       "^nsei",    "INDA",        "Asia-Pacific",
  "Bovespa",           "^BVSP",       "^bvp",     "EWZ",         "Latin America",
  "VIX (volatility)",  "^VIX",        "^vix",     NA_character_, "Volatility"
)
## `proxy` = US-listed backup ETF used ONLY as a last real-data resort when
## every direct source for the index fails. Country ETFs approximate their
## index (currency and holdings differ slightly) — the source table always
## shows when a proxy was used, so nothing happens silently.
## TOPIX note: ^TPX is not on Yahoo; 1475.T = iShares Core TOPIX ETF.

## ---- The SECTOR / THEME universe ----------------------------------------
## Themes are tracked through their most liquid ETF (identical fallback
## cascade works), plus native symbols for crypto and commodity futures.
sectors <- tibble::tribble(
  ~name,                          ~yahoo,     ~stooq,          ~proxy,        ~theme,
  "Quantum Computing (QTUM)",     "QTUM",     "qtum.us",       NA_character_, "Tech Frontier",
  "AI & Robotics (BOTZ)",         "BOTZ",     "botz.us",       "ROBO",        "Tech Frontier",
  "Semiconductors / AI HW (SMH)", "SMH",      "smh.us",        "SOXX",        "Tech Frontier",
  "Cybersecurity (CIBR)",         "CIBR",     "cibr.us",       "HACK",        "Tech Frontier",
  "Biotech (XBI)",                "XBI",      "xbi.us",        "IBB",         "Tech Frontier",
  "Space (ARKX)",                 "ARKX",     "arkx.us",       NA_character_, "Tech Frontier",
  "Defense & Aerospace (ITA)",    "ITA",      "ita.us",        "PPA",         "Cyclicals & Defense",
  "Financials (XLF)",             "XLF",      "xlf.us",        "VFH",         "Cyclicals & Defense",
  "Industrials (XLI)",            "XLI",      "xli.us",        "VIS",         "Cyclicals & Defense",
  "Energy broad (XLE)",           "XLE",      "xle.us",        "VDE",         "Energy",
  "Clean Energy (ICLN)",          "ICLN",     "icln.us",       "TAN",         "Energy",
  "Uranium & Nuclear (URA)",      "URA",      "ura.us",        "URNM",        "Energy",
  "Crude Oil WTI (CL=F)",         "CL=F",     "cl.f",          "USO",         "Commodities",
  "Gold (GLD)",                   "GLD",      "gld.us",        "IAU",         "Commodities",
  "Silver (SLV)",                 "SLV",      "slv.us",        "SIVR",        "Commodities",
  "Copper Miners (COPX)",         "COPX",     "copx.us",       NA_character_, "Commodities",
  "Rare Earths (REMX)",           "REMX",     "remx.us",       NA_character_, "Commodities",
  "Bitcoin",                      "BTC-USD",  "btcusd",        "IBIT",        "Crypto",
  "Ethereum",                     "ETH-USD",  "ethusd",        "ETHA",        "Crypto",
  "Solana",                       "SOL-USD",  NA_character_,   NA_character_, "Crypto"
)
## Sector proxies = near-identical competitor ETFs tracking the same theme
## (e.g. IAU backs up GLD, SOXX backs up SMH) — real data, same exposure.
```

```{r fetch-engine}
#| include: false

## ============================================================
##  DATA FETCH ENGINE v2 — reliability-first.
##  Up to 9 REAL sources per asset, every network call retried
##  3x with backoff. STRICT mode (the default) refuses to build
##  the report on anything but complete real data: if every real
##  source fails for any asset, the render ABORTS with a clear
##  error naming the culprits — so an incomplete or simulated
##  report can never be generated, let alone emailed.
##  Set env STRICT_DATA=false to re-enable the simulated fallback
##  (useful only for offline testing of the layout).
## ============================================================

UA <- "Mozilla/5.0 (Windows NT 10.0; Win64; x64) AppleWebKit/537.36"
STRICT_DATA <- !identical(tolower(Sys.getenv("STRICT_DATA", "true")), "false")
TIINGO_KEY  <- Sys.getenv("TIINGO_API_KEY", "")   # optional extra source

## Retry any flaky network call: 3 attempts, pausing 1s then 4s.
## Transient hiccups (rate limits, timeouts) are the #1 failure mode,
## so this alone eliminates most "source down" events.
with_retry <- function(fn, tries = 3, pause = c(1, 4)) {
  out <- NULL
  for (i in seq_len(tries)) {
    out <- tryCatch(fn(), error = function(e) e)
    if (!inherits(out, "error")) return(out)
    if (i < tries) Sys.sleep(pause[min(i, length(pause))])
  }
  stop(conditionMessage(out))
}

ohlc_ok <- function(x) !is.null(x) && nrow(x) >= 30

## --- Sources 1+2: Yahoo Finance v8 chart JSON (two independent hosts) ---
src_yahoo_json <- function(sym_yahoo, host = "query1", from = FROM_DATE) {
  if (is.na(sym_yahoo)) return(NULL)
  enc <- utils::URLencode(sym_yahoo, reserved = TRUE)
  url <- sprintf(
    "https://%s.finance.yahoo.com/v8/finance/chart/%s?period1=%d&period2=%d&interval=1d",
    host, enc, as.integer(as.POSIXct(from)), as.integer(Sys.time()))
  r <- httr::GET(url, httr::add_headers(`User-Agent` = UA), httr::timeout(20))
  if (httr::status_code(r) != 200) stop("HTTP ", httr::status_code(r))
  j <- jsonlite::fromJSON(httr::content(r, "text", encoding = "UTF-8"),
                          simplifyVector = FALSE)
  res <- j$chart$result[[1]]
  ts  <- as.numeric(unlist(res$timestamp))
  q   <- res$indicators$quote[[1]]
  nn  <- function(x) vapply(x, function(v) if (is.null(v)) NA_real_ else as.numeric(v), numeric(1))
  df  <- data.frame(Open = nn(q$open), High = nn(q$high),
                    Low = nn(q$low),  Close = nn(q$close),
                    Volume = nn(q$volume))
  x <- xts(df, order.by = as.Date(as.POSIXct(ts, origin = "1970-01-01")))
  x <- x[!is.na(x$Close), ]
  if (nrow(x) < 30) stop("too few rows")
  x
}

## --- Source 3: quantmod getSymbols(src="yahoo") -------------------------
src_quantmod_yahoo <- function(sym_yahoo, from = FROM_DATE) {
  if (is.na(sym_yahoo)) return(NULL)
  x <- quantmod::getSymbols(sym_yahoo, src = "yahoo", from = from,
                            auto.assign = FALSE, warnings = FALSE)
  colnames(x) <- c("Open","High","Low","Close","Volume","Adjusted")[seq_len(ncol(x))]
  if (nrow(x) < 30) stop("too few rows")
  x[, c("Open","High","Low","Close","Volume")]
}

## --- Source 4: quantmod getSymbols(src="stooq") -------------------------
src_quantmod_stooq <- function(sym_stooq, from = FROM_DATE) {
  if (is.na(sym_stooq)) return(NULL)
  x <- quantmod::getSymbols(sym_stooq, src = "stooq",
                            auto.assign = FALSE, warnings = FALSE)
  x <- x[paste0(from, "/")]
  colnames(x) <- c("Open","High","Low","Close","Volume")[seq_len(ncol(x))]
  if (nrow(x) < 30) stop("too few rows")
  x
}

## --- Source 5: direct Stooq CSV endpoint --------------------------------
src_stooq_csv <- function(sym_stooq, from = FROM_DATE) {
  if (is.na(sym_stooq)) return(NULL)
  url <- sprintf("https://stooq.com/q/d/l/?s=%s&i=d", sym_stooq)
  r <- httr::GET(url, httr::add_headers(`User-Agent` = UA), httr::timeout(20))
  txt <- httr::content(r, "text", encoding = "UTF-8")
  if (!grepl("^Date", txt)) stop("no CSV header (throttled?)")
  df <- utils::read.csv(text = txt)
  x <- xts(df[, c("Open","High","Low","Close",
                  if ("Volume" %in% names(df)) "Volume")],
           order.by = as.Date(df$Date))
  x <- x[paste0(from, "/")]
  if (nrow(x) < 30) stop("too few rows")
  x
}

## --- Source 6: Tiingo daily bars (activates when TIINGO_API_KEY is set) --
## Institutional-grade curated EOD data; free key allows 1,000 req/day —
## ample for this universe. Plain US tickers only (no ^indices / =F / .XX),
## so it primarily backs up the theme ETFs and the index ETF proxies.
src_tiingo <- function(sym, from = FROM_DATE) {
  if (!nzchar(TIINGO_KEY) || is.na(sym) || grepl("[\\^=.\\-]", sym)) return(NULL)
  url <- sprintf("https://api.tiingo.com/tiingo/daily/%s/prices?startDate=%s&token=%s",
                 tolower(sym), format(from), TIINGO_KEY)
  r <- httr::GET(url, httr::timeout(20))
  if (httr::status_code(r) != 200) stop("HTTP ", httr::status_code(r))
  j <- jsonlite::fromJSON(httr::content(r, "text", encoding = "UTF-8"))
  if (!is.data.frame(j) || !nrow(j)) stop("empty response")
  x <- xts(j[, c("open","high","low","close","volume")],
           order.by = as.Date(substr(j$date, 1, 10)))
  colnames(x) <- c("Open","High","Low","Close","Volume")
  if (nrow(x) < 30) stop("too few rows")
  x
}

## --- Source 9 (last real resort): FRED official close-only series -------
## The St. Louis Fed — about as reliable as data sources get. Close-only,
## so OHLC is collapsed to the close (trend metrics unaffected; candles
## degrade to bars) — which is why it sits LAST among the real sources.
FRED_MAP <- c("S&P 500" = "SP500", "Nasdaq Composite" = "NASDAQCOM",
              "Dow Jones" = "DJIA", "Nikkei 225" = "NIKKEI225",
              "VIX (volatility)" = "VIXCLS")
src_fred_close <- function(name, from = FROM_DATE) {
  if (is.na(name) || !(name %in% names(FRED_MAP))) return(NULL)
  x <- quantmod::getSymbols(FRED_MAP[[name]], src = "FRED", auto.assign = FALSE)
  x <- x[!is.na(x[, 1]), ]; x <- x[paste0(from, "/")]
  cl <- as.numeric(x[, 1])
  out <- xts(cbind(Open = cl, High = cl, Low = cl, Close = cl, Volume = 0),
             order.by = as.Date(index(x)))
  if (nrow(out) < 30) stop("too few rows")
  out
}

## --- Simulated fallback — DISABLED in strict mode -------------------------
## Kept only for offline layout testing (STRICT_DATA=false). Deterministic
## geometric Brownian motion seeded by symbol.
src_simulated <- function(sym_yahoo, from = FROM_DATE) {
  if (is.na(sym_yahoo) || !nzchar(sym_yahoo)) sym_yahoo <- "FALLBACK"
  seedn <- sum(utils::head(utils::adist(sym_yahoo, letters)[1, ], 5)) +
           nchar(sym_yahoo) * 7
  set.seed(seedn)
  days <- seq(from, Sys.Date(), by = "day")
  if (!grepl("-USD", sym_yahoo)) {               # crypto trades 7 days a week
    days <- days[!weekdays(days) %in% c("Saturday","Sunday")]
  }
  n <- length(days)
  base <- if (grepl("VIX", sym_yahoo)) 18
          else if (grepl("BTC", sym_yahoo)) 60000
          else if (grepl("-USD", sym_yahoo)) 2000
          else if (grepl("=F", sym_yahoo)) 75
          else if (grepl("\\^", sym_yahoo)) 3000 else 80
  drift <- if (grepl("VIX", sym_yahoo)) 0 else 0.0003
  vol   <- if (grepl("VIX", sym_yahoo)) 0.06
           else if (grepl("-USD", sym_yahoo)) 0.03 else 0.011
  ret <- rnorm(n, drift, vol)
  close <- base * cumprod(1 + ret)
  open  <- close / (1 + rnorm(n, 0, vol/3))
  high  <- pmax(open, close) * (1 + abs(rnorm(n, 0, vol/2)))
  low   <- pmin(open, close) * (1 - abs(rnorm(n, 0, vol/2)))
  volm  <- round(runif(n, 1e8, 5e8))
  xts(cbind(Open=open, High=high, Low=low, Close=close, Volume=volm),
      order.by = days)
}

## --- The cascade: up to 9 real attempts, each internally retried 3x ------
fetch_series <- function(row) {
  y  <- row$yahoo
  s  <- row$stooq
  pr <- if (!is.null(row$proxy)) row$proxy else NA_character_
  nm <- if (!is.null(row$name))  row$name  else NA_character_
  prs <- if (!is.na(pr)) paste0(tolower(pr), ".us") else NA_character_
  attempts <- list(
    list(name = "Yahoo v8 JSON",          fn = function() with_retry(function() src_yahoo_json(y, "query1"))),
    list(name = "Yahoo v8 JSON (host 2)", fn = function() with_retry(function() src_yahoo_json(y, "query2"))),
    list(name = "quantmod/Yahoo",         fn = function() with_retry(function() src_quantmod_yahoo(y))),
    list(name = "quantmod/Stooq",         fn = function() with_retry(function() src_quantmod_stooq(s))),
    list(name = "Stooq CSV",              fn = function() with_retry(function() src_stooq_csv(s))),
    list(name = "Tiingo",                 fn = function() with_retry(function() src_tiingo(y))),
    list(name = sprintf("Backup ETF %s (Yahoo)", pr), fn = function() with_retry(function() src_yahoo_json(pr, "query1"))),
    list(name = sprintf("Backup ETF %s (Stooq)", pr), fn = function() with_retry(function() src_stooq_csv(prs))),
    list(name = "FRED close-only",        fn = function() with_retry(function() src_fred_close(nm)))
  )
  for (a in attempts) {
    out <- tryCatch(a$fn(), error = function(e) NULL)
    if (ohlc_ok(out)) { attr(out, "source") <- a$name; return(out) }
  }
  if (STRICT_DATA) return(NULL)          # caller aborts the render loudly
  out <- src_simulated(y); attr(out, "source") <- "Simulated (demo)"; out
}

## --- Fetch BOTH universes; in strict mode, abort on ANY failure ----------
market <- list(); source_log <- character(0); failed_assets <- character(0)
for (i in seq_len(nrow(indices))) {
  s <- fetch_series(indices[i, ])
  if (is.null(s)) { failed_assets <- c(failed_assets, indices$name[i]); next }
  market[[indices$name[i]]] <- s
  source_log[indices$name[i]] <- attr(s, "source")
}

sector_data <- list(); sector_source_log <- character(0)
for (i in seq_len(nrow(sectors))) {
  s <- fetch_series(sectors[i, ])
  if (is.null(s)) { failed_assets <- c(failed_assets, sectors$name[i]); next }
  sector_data[[sectors$name[i]]] <- s
  sector_source_log[sectors$name[i]] <- attr(s, "source")
}

if (STRICT_DATA && length(failed_assets)) {
  stop("STRICT DATA MODE — render aborted so an incomplete report is never produced. ",
       "Every real source failed (after retries) for: ",
       paste(failed_assets, collapse = ", "), ". ",
       "This is almost always transient — re-run the workflow in a few minutes. ",
       "To allow simulated placeholders instead, set env STRICT_DATA=false.")
}

USING_DEMO <- length(source_log) > 0 &&
              all(c(source_log, sector_source_log) == "Simulated (demo)")
ANY_DEMO   <- any(c(source_log, sector_source_log) == "Simulated (demo)")
```

```{r indicators}
#| include: false

## ---- Per-series indicator computation -----------------------------------
calc_metrics <- function(x, name) {
  cl <- as.numeric(Cl(x)); dt <- index(x); n <- length(cl)
  last <- cl[n]
  sma50  <- if (n >= 50)  as.numeric(SMA(cl, 50))[n]  else NA
  sma200 <- if (n >= 200) as.numeric(SMA(cl, 200))[n] else NA
  rsi14  <- if (n >= 15)  as.numeric(RSI(cl, 14))[n]  else NA
  macd_df <- if (n >= 35) tryCatch(TTR::MACD(cl), error=function(e) NULL) else NULL
  macd_hist <- if (!is.null(macd_df)) as.numeric(macd_df[n,"macd"] - macd_df[n,"signal"]) else NA
  roc20 <- if (n >= 21) (last/cl[n-20]-1)*100 else NA
  roc60 <- if (n >= 61) (last/cl[n-60]-1)*100 else NA
  hi52 <- max(cl[dt >= (max(dt)-365)]); lo52 <- min(cl[dt >= (max(dt)-365)])
  from_hi <- (last/hi52 - 1)*100
  from_lo <- (last/lo52 - 1)*100
  ## golden / death cross over last 10 sessions
  cross <- "none"
  if (n >= 205) {
    s50 <- SMA(cl,50); s200 <- SMA(cl,200)
    d <- sign(s50 - s200); d <- d[!is.na(d)]
    if (length(d) > 11) {
      recent <- tail(d, 11)
      if (any(diff(recent) > 0)) cross <- "golden"
      if (any(diff(recent) < 0)) cross <- "death"
    }
  }
  ## 50d MA slope: rising vs 10 sessions ago?
  ma_rising <- NA
  if (n >= 60) {
    s50v <- as.numeric(SMA(cl, 50))
    ma_rising <- s50v[n] > s50v[n - 10]
  }
  ret1d <- if (n>=2) (last/cl[n-1]-1)*100 else NA
  data.frame(
    Index = name, Last = last, Ret1D = ret1d, ROC20 = roc20, ROC60 = roc60,
    RSI = rsi14, MACDhist = macd_hist,
    SMA50 = sma50, SMA200 = sma200,
    AboveSMA200 = ifelse(is.na(sma200), NA, last > sma200),
    FromHigh = from_hi, FromLow = from_lo, Cross = cross,
    MArising = ma_rising,
    stringsAsFactors = FALSE)
}

equity_names <- setdiff(names(market), "VIX (volatility)")
metrics <- do.call(rbind, lapply(equity_names,
             function(nm) calc_metrics(market[[nm]], nm)))
rownames(metrics) <- NULL

sector_metrics <- do.call(rbind, lapply(names(sector_data),
             function(nm) calc_metrics(sector_data[[nm]], nm)))
rownames(sector_metrics) <- NULL

## VIX helpers
vix_x <- market[["VIX (volatility)"]]
vix_last <- as.numeric(Cl(vix_x))[nrow(vix_x)]
vix_avg  <- mean(tail(as.numeric(Cl(vix_x)), 60), na.rm = TRUE)
```

```{r horizons}
#| include: false

## ============================================================
##  TIME-HORIZON MACHINERY
##  Backward: returns over 1w / 1m / 3m / 6m / 1y / 5y.
##  Forward:  one auto.arima fit per key asset, horizons read
##            off a single 252-step forecast (5/21/63/126/252).
##  No 5-year-ahead forecast on purpose — not reliable.
## ============================================================
HORIZONS <- c(`1 Week` = 7, `1 Month` = 30, `3 Months` = 91,
              `6 Months` = 182, `1 Year` = 365, `5 Years` = 1826)

## Business-day sequence: forecast steps are TRADING days, so plotting them on
## calendar days would land the "1 year ahead" mark at ~8.3 months on the axis.
next_bdays <- function(after, n) {
  d <- seq(after + 1, by = "day", length.out = ceiling(n * 1.6) + 7)
  head(d[!weekdays(d) %in% c("Saturday", "Sunday")], n)
}

ret_over <- function(x, days) {
  cl <- as.numeric(Cl(x)); dt <- index(x); n <- length(cl)
  idx <- which(dt <= (max(dt) - days))
  if (!length(idx)) return(NA_real_)
  (cl[n] / cl[max(idx)] - 1) * 100
}

all_series <- c(market[equity_names], sector_data)
horizon_tbl <- data.frame(Asset = names(all_series), stringsAsFactors = FALSE)
for (h in names(HORIZONS)) {
  horizon_tbl[[h]] <- vapply(all_series,
                             function(x) ret_over(x, HORIZONS[[h]]), numeric(1))
}
horizon_tbl$Type <- ifelse(horizon_tbl$Asset %in% indices$name, "Index", "Theme")

FC_STEPS <- c(`1 Week ahead` = 5, `1 Month ahead` = 21, `3 Months ahead` = 63,
              `6 Months ahead` = 126, `1 Year ahead` = 252)

horizon_forecast <- function(x, name, fit_len = 750) {
  cl <- as.numeric(Cl(x)); cl <- cl[!is.na(cl)]
  fit <- tryCatch(forecast::auto.arima(tail(cl, fit_len)), error = function(e) NULL)
  if (is.null(fit)) fit <- tryCatch(forecast::ets(tail(cl, fit_len)),
                                    error = function(e) NULL)
  if (is.null(fit)) return(NULL)
  fc <- forecast::forecast(fit, h = 252, level = c(80, 95))
  last <- tail(cl, 1)
  data.frame(Asset   = name,
             Horizon = names(FC_STEPS),
             Point   = round(as.numeric(fc$mean[FC_STEPS]), 2),
             `Chg %` = round((as.numeric(fc$mean[FC_STEPS]) / last - 1) * 100, 1),
             Lo95    = round(as.numeric(fc$lower[FC_STEPS, 2]), 2),
             Hi95    = round(as.numeric(fc$upper[FC_STEPS, 2]), 2),
             check.names = FALSE, stringsAsFactors = FALSE)
}
```

```{r trend-scores}
#| include: false

## ============================================================
##  SECTOR TREND SCORE (0-100) — trend-first by design, since
##  many themes trade disconnected from fundamental value.
##  Components (points):
##    15  price above 50d MA
##    15  price above 200d MA
##    10  50d MA above 200d MA (bullish alignment)
##    15  50d MA rising vs 10 sessions ago
##    15  ROC20 scaled from -10%..+10%  -> 0..15
##    20  ROC60 scaled from -20%..+20%  -> 0..20
##    10  proximity to 52w high: -30%..0% -> 0..10
## ============================================================
trend_score <- function(m) {
  clamp <- function(v, lo, hi) pmin(pmax(v, lo), hi)
  p <- 0
  p <- p + 15 * ifelse(is.na(m$SMA50),  0.5, as.numeric(m$Last > m$SMA50))
  p <- p + 15 * ifelse(is.na(m$SMA200), 0.5, as.numeric(m$Last > m$SMA200))
  p <- p + 10 * ifelse(is.na(m$SMA50) | is.na(m$SMA200), 0.5,
                       as.numeric(m$SMA50 > m$SMA200))
  p <- p + 15 * ifelse(is.na(m$MArising), 0.5, as.numeric(m$MArising))
  ## NA-safe: short histories get neutral credit instead of poisoning the score
  p <- p + 15 * ifelse(is.na(m$ROC20),    0.5, clamp((m$ROC20 + 10) / 20, 0, 1))
  p <- p + 20 * ifelse(is.na(m$ROC60),    0.5, clamp((m$ROC60 + 20) / 40, 0, 1))
  p <- p + 10 * ifelse(is.na(m$FromHigh), 0.5, clamp((m$FromHigh + 30) / 30, 0, 1))
  round(p)
}
sector_metrics$Trend <- trend_score(sector_metrics)

## ---- Relative strength vs S&P 500 (60-day change of ratio) --------------
spx_cl <- Cl(market[["S&P 500"]])
rel_strength_60d <- function(x) {
  merged <- merge(Cl(x), spx_cl, join = "inner")
  merged <- merged[complete.cases(merged), ]
  if (nrow(merged) < 61) return(NA_real_)
  ratio <- as.numeric(merged[,1]) / as.numeric(merged[,2])
  n <- length(ratio)
  (ratio[n] / ratio[n-60] - 1) * 100
}
sector_metrics$RSvsSPX60 <- vapply(sector_metrics$Index,
  function(nm) rel_strength_60d(sector_data[[nm]]), numeric(1))

## ---- Sector weather one-liners (pure if/else) ----------------------------
sector_weather <- function(s) {
  if (is.na(s))     c("❓",   "Not enough history yet to score this trend reliably.")
  else if (s >= 80) c("🔥☀️", "Blazing uptrend — momentum is hot; strong trends can persist but run fast when they break.")
  else if (s >= 65) c("📈🌤️", "Healthy uptrend — the wind is at this theme's back.")
  else if (s >= 50) c("➡️⛅", "Drifting sideways with a mild positive tilt.")
  else if (s >= 35) c("🌥️",  "Losing altitude — the trend is cooling; watch support levels.")
  else if (s >= 20) c("🌧️",  "Downtrend — assume rain until the tape proves otherwise.")
  else              c("🧊⛈️", "Deep freeze — falling and frozen out; wait for a thaw before wading in.")
}
sw <- t(vapply(sector_metrics$Trend, sector_weather, character(2)))
sector_metrics$Sky     <- sw[, 1]
sector_metrics$Reading <- sw[, 2]

## ---- Same weather treatment for the world indices ------------------------
## (identical scoring function, so index and theme skies are comparable)
metrics$Trend <- trend_score(metrics)
swi <- t(vapply(metrics$Trend, sector_weather, character(2)))
metrics$Sky     <- swi[, 1]
metrics$Reading <- swi[, 2]
```

```{r valuation}
#| include: false

## ---- Live valuation scrapes with fallbacks -----------------------------
scrape_multpl <- function(slug) {
  url <- paste0("https://www.multpl.com/", slug)
  tryCatch({
    h <- rvest::read_html(httr::content(
      httr::GET(url, httr::add_headers(`User-Agent`=UA), httr::timeout(20)), "text"))
    txt <- rvest::html_text(rvest::html_element(h, "#current"))
    as.numeric(gsub("[^0-9.]", "", regmatches(txt, regexpr("[0-9.]+", txt))))
  }, error = function(e) NA_real_)
}
cape <- scrape_multpl("shiller-pe")          # Shiller CAPE
pe   <- scrape_multpl("s-p-500-pe-ratio")    # trailing P/E
## Last-known-good fallbacks (refresh periodically): mid-2026 CAPE ~41.7, P/E ~29
if (is.na(cape)) cape <- 41.7
if (is.na(pe))   pe   <- 29.0

## Buffett Indicator proxy: FRED SP500 / GDP (WILL5000PR removed 2024-06-03)
buffett <- tryCatch({
  sp  <- getSymbols("SP500", src = "FRED", auto.assign = FALSE)
  gdp <- getSymbols("GDP",   src = "FRED", auto.assign = FALSE)
  spv  <- as.numeric(last(sp[!is.na(sp)]))
  gdpv <- as.numeric(last(gdp[!is.na(gdp)]))
  (spv / gdpv) * 100      # index-points-per-$bn proxy, NOT true % of GDP
}, error = function(e) NA_real_)

## Technical overboughtness across equity universe
pct_above200 <- mean(metrics$AboveSMA200, na.rm = TRUE) * 100
avg_rsi      <- mean(metrics$RSI, na.rm = TRUE)

## ---- Composite 0-100 valuation / overbought score ----------------------
sc_cape <- 100 * pmin(pmax((cape - 10) / (44 - 10), 0), 1)  # 10..44 range
sc_pe   <- 100 * pmin(pmax((pe   -  8) / (30 -  8), 0), 1)
sc_rsi  <- 100 * pmin(pmax((avg_rsi - 30) / (70 - 30), 0), 1)
sc_brd  <- pct_above200
composite <- round(0.35*sc_cape + 0.20*sc_pe + 0.20*sc_rsi + 0.25*sc_brd)

## ---- Fear/greed style gauge (0 fear .. 100 greed) ----------------------
fg_mom  <- 100 * pmin(pmax((mean(metrics$ROC20, na.rm=TRUE) + 8)/16, 0), 1)
fg_vol  <- 100 * pmin(pmax((vix_avg - vix_last)/vix_avg + 0.5, 0), 1)
fg_brd  <- pct_above200
fear_greed <- round((fg_mom + fg_vol + fg_brd)/3)
```

```{r macro-radar}
#| include: false

## ============================================================
##  🛰️ MACRO RADAR — three grown-up indicators, all free and
##  key-less, translated into plain English downstream:
##   1) Yield curve (10y − 2y Treasury) — the bond market's
##      recession alarm (FRED, no API key required)
##   2) Credit stress — junk bonds (HYG) vs quality bonds (LQD);
##      when lenders get nervous, this ratio rolls over first
##   3) S&P 500 drawdown — "how far underwater" from the peak
##  Plus HISTORICAL ODDS: honest win-rates computed from the
##  fetched data itself, so probabilities are empirical.
## ============================================================

## 1) Yield curve spread (10y − 2y), FRED — key-less
yield_curve <- tryCatch({
  d10 <- getSymbols("DGS10", src = "FRED", auto.assign = FALSE)
  d02 <- getSymbols("DGS2",  src = "FRED", auto.assign = FALSE)
  yc  <- merge(d10, d02, join = "inner"); yc <- yc[complete.cases(yc), ]
  s <- yc[, 1] - yc[, 2]; colnames(s) <- "Spread10y2y"
  tail(s, 1500)
}, error = function(e) NULL)
yc_now      <- if (!is.null(yield_curve)) as.numeric(last(yield_curve)) else NA_real_
yc_inverted <- isTRUE(yc_now < 0)

## 2) Credit stress proxy: HYG / LQD through the same fetch cascade
hyg <- fetch_series(list(yahoo = "HYG", stooq = "hyg.us"))
lqd <- fetch_series(list(yahoo = "LQD", stooq = "lqd.us"))
credit_demo <- any(c(attr(hyg, "source"), attr(lqd, "source")) == "Simulated (demo)")
credit_ratio <- tryCatch({
  m <- merge(Cl(hyg), Cl(lqd), join = "inner"); m <- m[complete.cases(m), ]
  r <- m[, 1] / m[, 2]; colnames(r) <- "HYGoverLQD"; r
}, error = function(e) NULL)
credit_stress <- FALSE; credit_roc20 <- NA_real_; credit_below200 <- NA
if (!is.null(credit_ratio) && nrow(credit_ratio) > 220) {
  cr  <- as.numeric(credit_ratio); ncr <- length(cr)
  cr200 <- as.numeric(SMA(cr, 200))[ncr]
  credit_roc20    <- (cr[ncr] / cr[ncr - 20] - 1) * 100
  credit_below200 <- cr[ncr] < cr200
  credit_stress   <- isTRUE(credit_below200) && isTRUE(credit_roc20 < 0)
}

## 3) Drawdown ("underwater") series for the S&P 500
spx_close <- as.numeric(Cl(market[["S&P 500"]]))
spx_dates <- index(Cl(market[["S&P 500"]]))
dd_series <- (spx_close / cummax(spx_close) - 1) * 100
dd_now    <- tail(dd_series, 1)

## 4) HISTORICAL ODDS — empirical win-rates over the fetched lookback
win_rate <- function(cl, k) {          # % of k-day windows that ended higher
  n <- length(cl); if (n <= k + 1) return(NA_real_)
  mean(cl[(k + 1):n] > cl[1:(n - k)], na.rm = TRUE) * 100
}
ODDS_WINDOWS <- c(`1 day` = 1, `1 week` = 5, `1 month` = 21,
                  `3 months` = 63, `6 months` = 126, `1 year` = 252)
odds_vals <- vapply(ODDS_WINDOWS, function(k) win_rate(spx_close, k), numeric(1))
coin_note <- function(p) {
  if (is.na(p)) "…"
  else if (p >= 85) "🎯 Very strong odds — but never a guarantee"
  else if (p >= 70) "👍 Clearly better than a coin flip"
  else if (p >= 55) "🪙 A slightly loaded coin, nothing more"
  else if (p >= 45) "🪙 Basically a coin flip"
  else "👎 Worse than a coin flip over this stretch"
}
odds_tbl <- data.frame(
  `If you had picked a random...` = paste0(names(ODDS_WINDOWS), " window"),
  `Chance it ended higher` = sprintf("%.0f%%", odds_vals),
  `In plain English` = vapply(odds_vals, coin_note, character(1)),
  check.names = FALSE)

## Conditional odds: does the 200-day average actually matter? Show, don't tell.
sma200v  <- as.numeric(SMA(spx_close, 200))
n_spx    <- length(spx_close)
fwd21    <- rep(NA_real_, n_spx)
fwd21[1:(n_spx - 21)] <- spx_close[22:n_spx] / spx_close[1:(n_spx - 21)] - 1
above_ma <- !is.na(sma200v) & spx_close > sma200v
below_ma <- !is.na(sma200v) & spx_close <= sma200v
odds_above <- mean(fwd21[above_ma] > 0, na.rm = TRUE) * 100
odds_below <- mean(fwd21[below_ma] > 0, na.rm = TRUE) * 100
regime_above_now <- isTRUE(spx_close[n_spx] > sma200v[n_spx])
```

```{r bear-watch-calc}
#| include: false

## ============================================================
##  🐻 BEAR WATCH — explicit warning lights, always checked.
## ============================================================
sp_row  <- metrics[metrics$Index == "S&P 500", ]
gold_rs <- sector_metrics$RSvsSPX60[sector_metrics$Index == "Gold (GLD)"]
btc_roc <- sector_metrics$ROC20[sector_metrics$Index == "Bitcoin"]
near_hi_weak <- isTRUE(sp_row$FromHigh > -3) && !is.na(sp_row$RSI) && sp_row$RSI < 55

bear_signals <- data.frame(
  Signal = c(
    "S&P 500 below its 200-day average (long-term trend broken)",
    "S&P 500 in correction territory (>10% off its high)",
    "S&P 500 in a bear market (>20% off its high)",
    "Fewer than half of world indices above their 200-day average (breadth broken)",
    "Recent death cross in one or more major indices",
    "VIX at or above 25 (storm-force winds)",
    "VIX spiking >20% above its 60-day average (fear accelerating)",
    "Average 20-day momentum across world indices is negative",
    "Weak internals: S&P near its high but RSI soft (negative-divergence proxy)",
    "Safe-haven rotation: gold beating stocks while stocks fall",
    "Risk appetite draining: Bitcoin down >15% in a month",
    "Composite heat score >= 70 — overheated markets fall hardest",
    "Recession radar: yield curve inverted (10y under 2y — the bond market bracing for trouble)",
    "Credit stress: junk bonds losing to quality bonds (HYG/LQD below trend and falling)"),
  Triggered = c(
    !isTRUE(sp_row$AboveSMA200),
    isTRUE(sp_row$FromHigh <= -10),
    isTRUE(sp_row$FromHigh <= -20),
    pct_above200 < 50,
    any(metrics$Cross == "death"),
    vix_last >= 25,
    vix_last > 1.2 * vix_avg,
    mean(metrics$ROC20, na.rm = TRUE) < 0,
    near_hi_weak,
    isTRUE(gold_rs > 0) && isTRUE(sp_row$ROC20 < 0),
    isTRUE(btc_roc < -15),
    composite >= 70,
    yc_inverted,
    credit_stress && !credit_demo),
  stringsAsFactors = FALSE)
bear_signals$Triggered[is.na(bear_signals$Triggered)] <- FALSE
bear_total <- nrow(bear_signals)
bear_score <- round(mean(bear_signals$Triggered) * 100)
bear_n     <- sum(bear_signals$Triggered)

## Bear alert tiers — pure if/else, plain English
bear_tier <- function(score, n, total = bear_total) {
  if (score >= 60) list(col = "#d9635b", icon = "🐻⛈️🚨",
    head = sprintf("BEAR ALERT — %d of %d warning lights are ON", n, total),
    body = "This is what the early-to-middle innings of serious downturns look like. Capital preservation beats bravado here: storms of this kind can intensify quickly and the exits get crowded.")
  else if (score >= 40) list(col = PAL$coral_deep, icon = "🐻🌧️",
    head = sprintf("High bear risk — %d of %d warning lights are ON", n, total),
    body = "Multiple independent warning systems are flashing at once. Historically, clusters like this precede the market's worst stretches more often than random chance. Tighten risk now, not after the fact.")
  else if (score >= 25) list(col = "#f7b98b", icon = "🐻⚠️",
    head = sprintf("Caution — %d of %d warning lights are ON", n, total),
    body = "Cracks are forming under a market that may still look fine on the surface. This is the zone where complacency costs the most — small hedges are cheap while skies are only partly cloudy.")
  else if (score >= 10) list(col = PAL$butter_deep, icon = "🐻👀",
    head = sprintf("Watchful — %d of %d warning lights are ON", n, total),
    body = "Mostly clear, but never mistake calm for safety: the biggest single-day storms in history arrived with few warning lights on. Keep the checklist in view.")
  else list(col = PAL$seafoam_deep, icon = "🌤️🛡️",
    head = sprintf("Bear checklist: all clear — %d of %d warning lights on", n, total),
    body = "No structural damage detected. Even so, remember the standing rule: risk is highest exactly when it feels lowest. An all-clear is a snapshot, not a promise.")
}
bt <- bear_tier(bear_score, bear_n, bear_total)
```

# ☀️ Executive Weather Summary

```{r banner, results='asis'}
#| echo: false
if (USING_DEMO) {
  cat('<div style="background:#f4837d;color:#fff;padding:14px;border-radius:16px;font-weight:bold;box-shadow:0 4px 14px rgba(244,131,125,.35);">',
      '⚠️ OFFLINE / DEMO MODE — every live source failed, so this report is built entirely on <em>simulated</em> data. Numbers below are illustrative only.',
      '</div>')
} else if (ANY_DEMO) {
  cat('<div style="background:#ffd3b6;color:#2f4858;padding:12px;border-radius:16px;box-shadow:0 4px 14px rgba(255,211,182,.5);">',
      '⚠️ Partial data: some series fell back to simulated demo data. See the source tables below.',
      '</div>')
} else {
  cat('<div style="background:#a8e6cf;color:#2f4858;padding:12px;border-radius:16px;box-shadow:0 4px 14px rgba(86,197,168,.35);">',
      '✅ Live data successfully retrieved for all indices and sectors. Strict mode guarantees this report contains only complete, real data — it refuses to build otherwise.',
      '</div>')
}
```

```{r tldr, results='asis'}
#| echo: false

## ---- 10-second TL;DR card: four traffic lights, zero jargon -------------
tl <- function(v, warm, hot) if (v >= hot) "🔴" else if (v >= warm) "🟡" else "🟢"
hot1 <- sector_metrics[order(-sector_metrics$Trend), ][1, ]
mood_word <- if (fear_greed >= 75) "greedy 😀" else if (fear_greed >= 55) "optimistic 🙂" else if (fear_greed >= 45) "balanced 😐" else if (fear_greed >= 25) "nervous 😟" else "fearful 😱"
odds_1m <- odds_vals[["1 month"]]
cat(sprintf('<div style="border:3px solid #a8e6cf;border-radius:20px;padding:16px;margin-top:14px;background:linear-gradient(135deg,#f2fbf8 0%%,#eef8fd 100%%);box-shadow:0 6px 18px rgba(129,207,232,.25);">
<b style="font-size:1.2em;">⚡ The whole report in 10 seconds</b>
<table style="width:100%%;margin-top:8px;font-size:1.05em;">
<tr><td>%s <b>Market heat</b></td><td>%d / 100 — how expensive &amp; stretched things are (higher = hotter = riskier)</td></tr>
<tr><td>%s <b>Bear risk</b></td><td>%d of %d warning lights ON (%d%%) — how many storm alarms are ringing</td></tr>
<tr><td>%s <b>Investor mood</b></td><td>%d / 100 — the crowd is currently %s</td></tr>
<tr><td>🎲 <b>Base rate</b></td><td>Over the last ~5½ years, a random 1-month bet on the S&amp;P 500 paid off <b>%.0f%%</b> of the time</td></tr>
<tr><td>🔥 <b>Hottest theme</b></td><td>%s %s (trend %d/100)</td></tr>
</table>
<p style="margin:8px 0 0 0;font-size:0.9em;opacity:0.8;">🟢 = comfortable · 🟡 = pay attention · 🔴 = high alert. Every number is explained below in plain words.</p>
</div>',
  tl(composite, 55, 70), composite,
  tl(bear_score, 25, 40), bear_n, bear_total, bear_score,
  if (fear_greed >= 75 || fear_greed <= 25) "🔴" else if (fear_greed >= 60 || fear_greed <= 40) "🟡" else "🟢", fear_greed, mood_word,
  odds_1m,
  hot1$Sky, hot1$Index, hot1$Trend))
```

::: {.callout-tip collapse="true" icon="false"}
## 🎓 New here? The 60-second decoder ring (tap to open)

No finance degree needed — the whole report runs on five ideas:

- **📏 200-day average ("the trend line").** The average price over the last ~10 months. Price *above* it = long-term uptrend ☀️; *below* it = long-term downtrend 🌧️. That's it.
- **🌀 RSI ("the speedometer", 0–100).** How fast price has been moving lately. Above 70 = sprinting (often due for a breather); below 30 = collapsed (often due for a bounce); ~50 = cruising.
- **💨 VIX ("the wind speed").** How violently traders expect prices to swing. Under 20 = calm breeze; over 30 = storm winds.
- **🗺️ Breadth ("how many boats are floating").** The % of world markets in an uptrend. If the S&P rises but breadth is weak, one big boat is hiding a sinking fleet.
- **🎲 The 95% band ("19 times out of 20").** Whenever you see a forecast range, read it as: *the model expects the price to land inside this range 19 times out of 20.* The wider the band, the more honest the model is being about not knowing.

**Golden rule of the whole report:** nothing here predicts the future. Everything is either *what already happened* (facts), *what usually happened after similar setups* (probabilities), or *a model's guess with honest error bars* (forecasts — trust them less the further out they go).
:::

```{r weather-text, results='asis'}
#| echo: false

## ---- The plain-English weather engine (pure if/else) -------------------
weather <- function(score, fg, vix, vixavg, breadth) {
  if (score >= 85) { icon <- "⛈️🌪️"; head <- "SEVERE STORM WARNING"
    body <- "Markets look dangerously overheated. Valuations are in the top of their historical range and momentum is stretched. Umbrellas up — sudden downpours (corrections) are common from here." }
  else if (score >= 70) { icon <- "🌧️"; head <- "Stormy & overbought"
    body <- "The sky is heavy. Prices are rich versus history and breadth is wide, a classic late-cycle look. Enjoy the warmth but keep a raincoat handy." }
  else if (score >= 55) { icon <- "⛅"; head <- "Warm with building clouds"
    body <- "Pleasant but pricey. The market is above fair-weather averages; not a storm yet, but the barometer is drifting down." }
  else if (score >= 40) { icon <- "🌤️"; head <- "Mild and mostly fair"
    body <- "Comfortable conditions. Valuations and momentum sit near their long-run middle — neither cheap nor expensive." }
  else if (score >= 25) { icon <- "☁️"; head <- "Cool and overcast"
    body <- "A grey, cautious mood. Prices are below trend and enthusiasm is muted — the kind of chilly weather that sometimes precedes clear skies." }
  else { icon <- "🌦️❄️"; head <- "Cold snap / washout"
    body <- "Deep chill. Markets are beaten down and fearful. Historically, the coldest days have offered the warmest long-term entry points — but frostbite is real." }

  mood <- if (fg >= 75) "😀 Investors are downright greedy."
    else if (fg >= 55) "🙂 Mood tilts optimistic."
    else if (fg >= 45) "😐 Sentiment is balanced."
    else if (fg >= 25) "😟 Nervousness is creeping in."
    else "😱 Outright fear grips the tape."

  vixline <- if (vix >= 30) "🌪️ The volatility 'wind speed' (VIX) is howling — brace for turbulence."
    else if (vix >= 20) "💨 Winds (VIX) are gusty and above their calm-weather average."
    else if (vix < vixavg) "🍃 Winds (VIX) are light and below average — calm seas."
    else "🍃 Winds (VIX) are moderate."

  brd <- sprintf("🗺️ Breadth check: %.0f%% of world indices are above their 200-day average.", breadth)

  cat(sprintf('<div style="border:3px solid #81cfe8;border-radius:20px;padding:20px;margin-top:14px;background:#ffffff;box-shadow:0 6px 18px rgba(129,207,232,.25);">
  <div style="font-size:2.4em;">%s</div>
  <h2 style="margin:4px 0;">%s</h2>
  <p style="font-size:1.15em;">%s</p>
  <p>%s</p><p>%s</p><p>%s</p></div>',
  icon, head, body, mood, vixline, brd))
}
weather(composite, fear_greed, vix_last, vix_avg, pct_above200)
```

```{r bear-box, results='asis'}
#| echo: false
active <- bear_signals$Signal[bear_signals$Triggered]
active_html <- if (length(active))
  paste0("<ul style='margin:6px 0 0 0;'>",
         paste(sprintf("<li>⚠️ %s</li>", active), collapse = ""), "</ul>")
else "<p style='margin:6px 0 0 0;'>No active warning signals right now.</p>"
cat(sprintf('<div style="background:%s;color:#fff;padding:16px;border-radius:12px;margin-top:12px;">
<div style="font-size:1.6em;">%s</div>
<h3 style="margin:4px 0;color:#fff;">%s</h3>
<p style="margin:4px 0;">%s</p>%s
<p style="margin-top:8px;font-size:0.9em;opacity:0.85;">Full checklist, thresholds and what would flip this report bearish: see the 🐻 Bear Watch section.</p></div>',
  bt$col, bt$icon, bt$head, bt$body, active_html))
```

```{r hot-cold, results='asis'}
#| echo: false
## One-glance hottest / coldest themes, fed by the sector trend scores
sm <- sector_metrics[order(-sector_metrics$Trend), ]
hot  <- head(sm, 3); cold <- tail(sm, 3)
cat(sprintf('<div style="border:2px dashed #56c5a8;border-radius:16px;padding:12px;margin-top:10px;background:#f2fbf8;">
<b>🔥 Hottest themes right now:</b> %s<br>
<b>🧊 Coldest themes right now:</b> %s</div>',
  paste(sprintf("%s %s (%d)", hot$Sky, hot$Index, hot$Trend), collapse = " · "),
  paste(sprintf("%s %s (%d)", cold$Sky, cold$Index, cold$Trend), collapse = " · ")))
```

```{r gauge}
#| echo: false
gcol <- if (composite >= 70) PAL$coral_deep else if (composite >= 40) PAL$butter_deep else PAL$seafoam_deep
plot_ly(
  type = "indicator", mode = "gauge+number",
  value = composite,
  title = list(text = "Overall Market 'Heat' Score (0 = cold/cheap, 100 = overheated)"),
  gauge = list(
    axis = list(range = list(0, 100)),
    bar  = list(color = gcol),
    steps = list(
      list(range = c(0,25),  color = PAL$seafoam),
      list(range = c(25,40), color = "#d9f4ea"),
      list(range = c(40,55), color = PAL$butter),
      list(range = c(55,70), color = PAL$peach),
      list(range = c(70,85), color = PAL$coral),
      list(range = c(85,100),color = "#f4837d")),
    threshold = list(line = list(color = "black", width = 4),
                     thickness = 0.8, value = composite))
) |> pastel_layout(margin = list(t = 60, b = 10))
```

# 🎲 What Are the Chances?

Forget predictions for a moment — here are the **actual historical odds**, computed live from the ~5½ years of S&P 500 data this report just downloaded. No model, no opinion: just counting.

```{r odds-table}
#| echo: false
datatable(odds_tbl, rownames = FALSE, options = list(dom = "t"),
          caption = "Empirical win-rates: of ALL possible windows of each length in the fetched data, what share ended with the S&P 500 higher than it started?")
```

```{r odds-text, results='asis'}
#| echo: false
cat(sprintf("**The single most useful pattern in this whole report** 📏 — the 200-day trend line genuinely changes the odds:\n\n"))
cat(sprintf("- When the S&P 500 was **above** its 200-day average ☀️, the next month was positive **%.0f%%** of the time.\n", odds_above))
cat(sprintf("- When it was **below** 🌧️, the next month was positive only **%.0f%%** of the time.\n\n", odds_below))
cat(sprintf("**Right now the market is %s its trend line**, so history says the wind is currently %s.\n\n",
    ifelse(regime_above_now, "☀️ ABOVE", "🌧️ BELOW"),
    ifelse(regime_above_now, "at its back 🍃", "in its face 💨")))
cat("🐻 *Honest footnote: these odds come from one ~5½-year sample that includes whatever regime we happen to be in. They are real, but they are weather statistics, not laws of physics — a 70% chance of sunshine still rains 3 days in 10.*\n")
```

# ⏳ The Market Through Time

The same market looks completely different depending on how far you zoom out. Each subsection below reads one window of time — what happened over that lookback, and (except for 5 years) what the models project over the *same distance ahead*. Forecast confidence shrinks fast as the horizon grows: **1 week/1 month are usable, 3 months is soft, 6 months is indicative, 1 year is directional at best — and 5 years ahead is deliberately not forecast at all.**

```{r horizon-heatmap}
#| echo: false
hz <- names(HORIZONS)
zmat <- as.matrix(horizon_tbl[, hz])
rownames(zmat) <- horizon_tbl$Asset
zcap <- pmax(pmin(zmat, 60), -60)     # cap colors at +/-60% so 5y doesn't wash out the scale
plot_ly(x = hz, y = rownames(zmat), z = round(zcap, 1),
        customdata = round(zmat, 1),
        hovertemplate = "%{y}<br>%{x}: %{customdata}%<extra></extra>",
        type = "heatmap",
        colors = pastel_diverge,
        zmin = -60, zmax = 60) |>
  pastel_layout(title = "Return heatmap across time horizons (green = up, red = down; color capped at ±60%)",
         margin = list(l = 200), height = 700)
```

```{r time-sections, results='asis'}
#| echo: false

## Key assets that get forward projections in every time section
key_assets <- unique(c("S&P 500", "Nasdaq Composite", "Gold (GLD)", "Bitcoin",
                       sector_metrics$Index[order(-sector_metrics$Trend)][1]))
fc_all <- do.call(rbind, lapply(key_assets, function(nm) {
  x <- if (nm %in% names(market)) market[[nm]] else sector_data[[nm]]
  horizon_forecast(x, nm)
}))

section_meta <- list(
  list(h = "5 Years",  fc = NA_character_,
       note = "🚫🔮 **No 5-year forecast is shown — on purpose.** Statistical models at that range produce decoration, not information; anyone selling you a confident 5-year number is selling confidence, not analysis."),
  list(h = "1 Year",   fc = "1 Year ahead",
       note = "⚠️ The 1-year projection is included as requested, but it is **directional at best** — look at how wide the 95% band is. That width *is* the honest forecast. 🐻 Bear note: a full year is long enough to contain an entire correction that shorter windows won't see coming."),
  list(h = "6 Months", fc = "6 Months ahead",
       note = "6-month projections are indicative only. 🐻 Bear note: most historical drawdowns went from 'fine' to 'bear market' in less than six months."),
  list(h = "3 Months", fc = "3 Months ahead",
       note = "🐻 Bear note: a quarter is the classic span of a sharp correction — if warning lights are on in Bear Watch, this is the window where they usually bite."),
  list(h = "1 Month",  fc = "1 Month ahead",
       note = ""),
  list(h = "1 Week",   fc = "1 Week ahead",
       note = "One week is noise more often than signal — never extrapolate a weekly move into a story.")
)

horizon_mood <- function(med) {
  if (is.na(med))      "…"
  else if (med <= -10) "🐻⛈️ **Broad damage over this window** — a genuine storm passed through. Downtrends deserve respect: they end on evidence, not hope."
  else if (med <= -3)  "🐻🌧️ **Bearish tilt** — more assets fell than rose over this window. Caution is the default setting here."
  else if (med < 3)    "⛅ Mixed and range-bound — no dominant weather system over this window."
  else if (med < 10)   "🌤️ Constructive — most assets gained. 🐻 But note: calm windows are exactly where complacency compounds; keep one eye on the Bear Watch checklist."
  else                 "🔥☀️ Very hot — big, broad gains. 🐻 **Standing bear warning:** heat like this rarely persists, and the strongest stretches historically cluster right before squalls. Strength is not safety."
}

for (m in section_meta) {
  cat(sprintf("\n\n## %s\n\n", m$h))
  vals <- horizon_tbl[[m$h]]
  med  <- median(vals, na.rm = TRUE)
  cat(horizon_mood(med), "\n\n")
  ok  <- which(!is.na(vals))
  ord <- ok[order(-vals[ok])]
  top <- head(ord, 3); bot <- rev(tail(ord, 3))
  cat(sprintf("**Best:** %s. **Worst:** %s.\n\n",
    paste(sprintf("%s (%+.1f%%)", horizon_tbl$Asset[top], vals[top]), collapse = ", "),
    paste(sprintf("%s (%+.1f%%)", horizon_tbl$Asset[bot], vals[bot]), collapse = ", ")))
  sub <- data.frame(Asset = horizon_tbl$Asset, Type = horizon_tbl$Type,
                    `Return %` = round(vals, 1), check.names = FALSE)
  sub <- sub[order(-sub$`Return %`, na.last = TRUE), ]
  print(htmltools::tagList(datatable(sub, rownames = FALSE,
        options = list(pageLength = 8, dom = "tp"))))
  if (!is.na(m$fc) && !is.null(fc_all)) {
    f <- fc_all[fc_all$Horizon == m$fc, c("Asset","Point","Chg %","Lo95","Hi95")]
    cat(sprintf("\n\n**Looking %s ahead** (auto.arima point forecasts with 95%% bands, key assets):\n\n",
                tolower(m$h)))
    print(htmltools::tagList(datatable(f, rownames = FALSE, options = list(dom = "t"))))
  }
  if (nzchar(m$note)) cat("\n\n", m$note, "\n\n")
}
```

# 🐻 Bear Watch

Bull markets get plenty of cheerleaders; this section exists to argue the other side, every single run. Fourteen independent warning lights are checked automatically — trend breaks, breadth, volatility, divergences, safe-haven rotation, risk appetite, and now the two macro alarms from the Recession & Credit Radar (yield-curve inversion and credit stress). **None of them predicts a crash on its own; it is the *cluster* that matters.** Think of each light as one smoke detector in a large house: one beeping is probably burnt toast 🍞; five beeping at once means leave the building 🏃.

```{r bear-gauge}
#| echo: false
bcol <- if (bear_score >= 60) "#d9635b" else if (bear_score >= 40) PAL$coral_deep else if (bear_score >= 25) "#f7b98b" else if (bear_score >= 10) PAL$butter_deep else PAL$seafoam_deep
plot_ly(type = "indicator", mode = "gauge+number",
  value = bear_score,
  title = list(text = "Bear Risk Score (share of warning lights ON)"),
  gauge = list(axis = list(range = list(0, 100)),
    bar = list(color = bcol),
    steps = list(
      list(range = c(0,10),  color = "#d9f4ea"),
      list(range = c(10,25), color = PAL$butter),
      list(range = c(25,40), color = PAL$peach),
      list(range = c(40,60), color = PAL$coral),
      list(range = c(60,100),color = "#f4837d")))) |>
  pastel_layout(margin = list(t = 60, b = 10))
```

```{r bear-table}
#| echo: false
btab <- data.frame(Light = ifelse(bear_signals$Triggered, "🔴 ON", "🟢 off"),
                   `Warning signal` = bear_signals$Signal, check.names = FALSE)
datatable(btab, rownames = FALSE, options = list(pageLength = 14, dom = "t"),
          caption = sprintf("The %d-light bear checklist, evaluated live on every render.", bear_total))
```

```{r bear-narrative, results='asis'}
#| echo: false
cat(sprintf("**Current reading: %s** — %s\n\n", bt$head, bt$body))
cat("**What would flip this report outright bearish** (pre-written rules, not opinion):\n\n")
cat("- 📉 S&P 500 closing below its 200-day average **and** breadth under 50% — the trend regime flips.\n")
cat("- ☠️ A fresh death cross on the S&P 500 or Nasdaq while the VIX holds above 25.\n")
cat("- 🩸 A composite heat score ≥ 70 followed by a negative 20-day momentum turn — overheated *and* rolling over is the classic topping sequence.\n")
cat("- 🥇 Gold and the VIX rising together while equities fall — money running for shelter, not rotating.\n")
cat("- 🪙 Crypto down hard (>15%/month) alongside small caps lagging — the risk-appetite canaries going quiet first.\n\n")
cat("🐻 *Standing reminder: drawdowns are a feature of markets, not a malfunction. The S&P 500 has historically averaged an intra-year drawdown of roughly double digits even in positive years — position sizing, not prediction, is what survives them.*\n")
```

# 🛰️ Recession & Credit Radar

Three "grown-up" macro instruments most private investors never look at — translated into plain weather language. All three are free and key-less.

## 🏦 The bond market's recession alarm (yield curve)

Normally, lending money for 10 years pays more than lending for 2 (you're locked in longer). When that flips — the curve **inverts** — the bond market is effectively saying *"we expect trouble ahead."* Historically this alarm has rung before most US recessions, usually with a long delay.

```{r yield-curve-chart}
#| echo: false
if (!is.null(yield_curve)) {
  ycv <- as.numeric(yield_curve)
  plot_ly(x = index(yield_curve), y = ycv, type = "scatter", mode = "lines",
          name = "10y − 2y spread",
          line = list(color = PAL$ink)) |>
    pastel_layout(title = "Yield curve: 10-year minus 2-year Treasury yield (%). Below the red line = inverted = recession alarm ringing.",
           yaxis = list(title = "%"),
           shapes = list(list(type = "line",
             x0 = min(index(yield_curve)), x1 = max(index(yield_curve)),
             y0 = 0, y1 = 0, line = list(color = PAL$coral_deep, dash = "dash"))))
} else {
  cat("Yield-curve data (FRED DGS10 − DGS2) could not be fetched on this run — the chart is skipped, and the corresponding Bear Watch light stays off rather than guessing.")
}
```

```{r yield-curve-text, results='asis'}
#| echo: false
if (!is.na(yc_now)) {
  cat(if (yc_inverted)
    sprintf("🚨 **The alarm is ringing:** the curve is inverted at %.2f%%. In plain English: bond investors are paid *more* for short loans than long ones — a bet that rates (and the economy) will cool. 🐻 Important nuance: the lag between inversion and actual trouble has historically ranged from months to ~2 years, so this is a *seasonal forecast*, not tomorrow's weather.\n", yc_now)
  else if (yc_now < 0.5)
    sprintf("🟡 **Flat-ish at %+.2f%%** — the alarm isn't ringing, but the battery light is on. Curves this flat mean the bond market sees little runway; watch for a dip below zero.\n", yc_now)
  else
    sprintf("🟢 **Healthy slope at %+.2f%%** — the bond market is not bracing for recession. One less thing to worry about (today).\n", yc_now))
}
```

## 💳 Are lenders getting nervous? (credit stress)

Junk bonds (risky loans, tracked by HYG) versus quality bonds (safe loans, LQD). When investors happily hold risky debt, this ratio rises 🟢. When they quietly flee to safety, it rolls over 🔴 — and credit usually smells trouble **before** the stock market does. Think of it as the canary that works in a bank.

```{r credit-chart}
#| echo: false
if (!is.null(credit_ratio)) {
  crv <- as.numeric(credit_ratio)
  cr_sma <- as.numeric(SMA(crv, 200))
  plot_ly(x = index(credit_ratio), y = crv, type = "scatter", mode = "lines",
          name = "HYG / LQD") |>
    add_lines(x = index(credit_ratio), y = cr_sma, name = "200d average",
              line = list(color = "#b39ddb", dash = "dot")) |>
    pastel_layout(title = paste0("Credit-stress canary: junk bonds ÷ quality bonds",
                          if (credit_demo) " ⚠️ (built on simulated fallback data this run)" else ""),
           yaxis = list(title = "HYG / LQD ratio"), hovermode = "x unified")
} else {
  cat("Credit ratio could not be built on this run — chart skipped, Bear Watch light stays off.")
}
```

```{r credit-text, results='asis'}
#| echo: false
if (!is.na(credit_roc20)) {
  cat(if (credit_stress)
    sprintf("🔴 **The canary looks unwell:** risky bonds are below their trend line and fell %.1f%% vs quality bonds over the last month. Lenders are edging toward the exits — historically an early-warning pattern worth respecting.\n", abs(credit_roc20))
  else if (isTRUE(credit_below200))
    "🟡 **Slightly pale canary:** the ratio is below its long-term trend but not actively falling. Worth a glance each week, not a panic.\n"
  else
    sprintf("🟢 **The canary is singing:** investors are comfortable holding risky debt (ratio %+.1f%% over the last month, above trend). Credit sees no storm on the radar.\n", credit_roc20))
  if (credit_demo) cat("\n⚠️ *Caveat: one or both bond series fell back to simulated data this run, so this reading is illustrative only and was excluded from the Bear Watch count.*\n")
}
```

## 🤿 How far underwater? (drawdown)

The most intuitive risk chart that exists: at every moment, how far below its **all-time-high-so-far** was the S&P 500? Zero = at a record high 🏔️. Every dip below zero is time spent "underwater" — this is what owning stocks actually *feels* like.

```{r drawdown-chart}
#| echo: false
plot_ly(x = spx_dates, y = dd_series, type = "scatter", mode = "lines",
        fill = "tozeroy", fillcolor = "rgba(244,131,125,0.30)",
        line = list(color = PAL$coral_deep), name = "Drawdown %") |>
  pastel_layout(title = "S&P 500 — % below its running record high ('the underwater chart')",
         yaxis = list(title = "% below peak"),
         shapes = list(
           list(type = "line", x0 = min(spx_dates), x1 = max(spx_dates),
                y0 = -10, y1 = -10, line = list(color = PAL$butter_deep, dash = "dot")),
           list(type = "line", x0 = min(spx_dates), x1 = max(spx_dates),
                y0 = -20, y1 = -20, line = list(color = "red", dash = "dot"))))
```

```{r drawdown-text, results='asis'}
#| echo: false
worst_dd <- min(dd_series, na.rm = TRUE)
pct_under10 <- mean(dd_series <= -10, na.rm = TRUE) * 100
cat(sprintf("**Right now:** the S&P 500 is **%.1f%%** below its record high %s\n\n",
    abs(dd_now),
    if (dd_now > -3) "— essentially at the surface 🏔️😎."
    else if (dd_now > -10) "— a normal dip 🌊, the kind markets produce almost every year."
    else if (dd_now > -20) "— officially a **correction** 🤿 (10–20% down). Uncomfortable, historically common."
    else "— officially a **bear market** 🐻🌊 (20%+ down). Painful, and historically also where long-term returns were born."))
cat(sprintf("**Perspective from this dataset:** the deepest dive of the last ~5½ years was **%.0f%%**, and the market spent about **%.0f%%** of all days at least 10%% underwater. Feeling seasick occasionally is the admission price of equity returns — the orange (−10%%) and red (−20%%) lines are there to show how routine it is.\n", abs(worst_dd), pct_under10))
```

# 🌍 World Indices Dashboard

```{r source-table}
#| echo: false
src_df <- data.frame(Index = names(source_log), Source = unname(source_log))
datatable(src_df, rownames = FALSE, options = list(pageLength = 5, dom = "tp"),
          caption = "Which data source succeeded for each index (fallback cascade result).")
```

```{r dash-table}
#| echo: false
show <- metrics |>
  transmute(` ` = Sky, Index,
            `Trend (0-100)` = Trend,
            Last = round(Last, 2),
            `1D %` = round(Ret1D, 2),
            `20D %` = round(ROC20, 2),
            RSI = round(RSI, 1),
            `% vs 200d MA` = round((Last/SMA200 - 1)*100, 1),
            `% from 52w High` = round(FromHigh, 1),
            Cross,
            `In plain English` = Reading)
datatable(show, rownames = FALSE,
          options = list(pageLength = 12, order = list(list(2, "desc"))),
          caption = "Live technical snapshot with the same weather scoring as the sector radar (0 = deep freeze, 100 = blazing). Sort any column.") |>
  formatStyle("1D %", color = styleInterval(0, c(PAL$down, PAL$up))) |>
  formatStyle("Trend (0-100)",
              background = styleColorBar(c(0, 100), PAL$sky),
              backgroundSize = "95% 70%",
              backgroundRepeat = "no-repeat",
              backgroundPosition = "center")
```

```{r norm-chart}
#| echo: false
## Normalized performance (rebased to 100) for a readable comparison
pick <- c("S&P 500","Nasdaq Composite","FTSE 100","DAX","Nikkei 225","Hang Seng")
pick <- intersect(pick, names(market))
p <- plot_ly()
for (nm in pick) {
  cl <- Cl(market[[nm]]); cl <- cl[!is.na(cl)]
  reb <- as.numeric(cl)/as.numeric(cl[1])*100
  p <- add_lines(p, x = index(cl), y = reb, name = nm)
}
p |> pastel_layout(title = "Normalized performance (rebased to 100)",
            yaxis = list(title = "Index = 100 at start"),
            hovermode = "x unified")
```

# 📊 Regional Deep Dives

```{r regional, results='asis'}
#| echo: false
for (reg in c("North America","Europe","Asia-Pacific","Latin America")) {
  nm_reg <- intersect(indices$name[indices$region == reg], names(market))
  if (!length(nm_reg)) next
  cat(sprintf("\n\n## %s\n\n", reg))
  sub <- metrics[metrics$Index %in% nm_reg, ]
  print(htmltools::tagList(datatable(
    sub |> transmute(Index, Last=round(Last,1), `20D %`=round(ROC20,1),
                     RSI=round(RSI,1), Cross,
                     `% vs 200d`=round((Last/SMA200-1)*100,1)),
    rownames = FALSE, options = list(dom = "t", pageLength = 10))))
}
```

# 🧭 Sector & Theme Radar

Your watchlist — quantum, AI, space, energy, crypto, gold, silver, rare earths, oil, financials, industrials — plus the themes that complete the picture: **semiconductors** (the hardware side of the AI trade), **cybersecurity**, **defense & aerospace**, **uranium/nuclear**, **clean energy**, **copper** (the electrification metal) and **biotech**. Each theme is tracked through its most liquid ETF or native symbol, fetched through the same five-source fallback cascade. Because many of these trade on *story and flows* rather than earnings, this section is deliberately **trend-first**: the Trend Score below measures only price behaviour, not value.

```{r sector-sources}
#| echo: false
ssrc <- data.frame(Theme = names(sector_source_log), Source = unname(sector_source_log))
datatable(ssrc, rownames = FALSE, options = list(pageLength = 5, dom = "tp"),
          caption = "Data source that succeeded for each sector/theme.")
```

## 🌤️ The Sector Weather Map

```{r sector-map}
#| echo: false
smap <- sector_metrics[order(-sector_metrics$Trend), ] |>
  transmute(` ` = Sky, Theme = Index,
            `Trend (0-100)` = Trend,
            `20D %` = round(ROC20, 1),
            `60D %` = round(ROC60, 1),
            `RS vs S&P (60d)` = round(RSvsSPX60, 1),
            `% from 52w High` = round(FromHigh, 1),
            Forecast = Reading)
datatable(smap, rownames = FALSE,
          options = list(pageLength = 20, dom = "t"),
          caption = "Themes ranked by pure price trend. 'RS vs S&P' = 60-day change of the theme/S&P-500 ratio: positive means the theme is beating the broad market.") |>
  formatStyle("Trend (0-100)",
              background = styleColorBar(c(0, 100), PAL$sky),
              backgroundSize = "95% 70%",
              backgroundRepeat = "no-repeat",
              backgroundPosition = "center") |>
  formatStyle("RS vs S&P (60d)", color = styleInterval(0, c(PAL$coral_deep, PAL$seafoam_deep)))
```

## 📈 Theme performance, rebased

```{r sector-norm}
#| echo: false
p <- plot_ly()
for (nm in names(sector_data)) {
  cl <- Cl(sector_data[[nm]]); cl <- cl[!is.na(cl)]
  cl <- tail(cl, 252)                         # ~1 trading year for readability
  reb <- as.numeric(cl)/as.numeric(cl[1])*100
  vis <- if (nm %in% head(sector_metrics$Index[order(-sector_metrics$Trend)], 6)) TRUE else "legendonly"
  p <- add_lines(p, x = index(cl), y = reb, name = nm, visible = vis)
}
p |> pastel_layout(title = "Themes rebased to 100 (last ~12 months). Top-6 trends shown; click legend to toggle the rest.",
            yaxis = list(title = "Rebased = 100"),
            hovermode = "x unified")
```

## 💪 Relative strength vs the S&P 500

```{r sector-rs}
#| echo: false
rs <- sector_metrics[order(-sector_metrics$RSvsSPX60), ]
plot_ly(rs, x = ~RSvsSPX60, y = ~reorder(Index, RSvsSPX60), type = "bar",
        orientation = "h",
        marker = list(color = ifelse(rs$RSvsSPX60 >= 0, PAL$seafoam_deep, PAL$coral_deep))) |>
  pastel_layout(title = "60-day relative strength vs S&P 500 (%). Right = leading, left = lagging.",
         xaxis = list(title = "Ratio change, %"), yaxis = list(title = ""),
         margin = list(l = 200))
```

## 🔗 How the themes move together

```{r sector-cor}
#| echo: false
## Correlation of daily returns across themes (last 120 common sessions)
rets <- NULL
for (nm in names(sector_data)) {
  r <- dailyReturn(Cl(sector_data[[nm]]))
  colnames(r) <- nm
  rets <- if (is.null(rets)) r else merge(rets, r, join = "outer")
}
rets <- tail(rets[complete.cases(rets), ], 120)
if (nrow(rets) >= 30) {
  cm <- cor(rets)
  plot_ly(x = colnames(cm), y = rownames(cm), z = round(cm, 2),
          type = "heatmap", colors = colorRamp(c(PAL$sky_deep, "#ffffff", PAL$coral_deep)),
          zmin = -1, zmax = 1) |>
    pastel_layout(title = "Correlation of daily returns (last ~120 sessions). Red = moves together, blue = moves opposite.",
           margin = list(l = 180, b = 160))
} else {
  cat("Not enough overlapping history to compute a stable correlation matrix.")
}
```

## 🔮 Sector forecasts (top trends + Bitcoin)

```{r sector-forecast}
#| echo: false
fc_names <- unique(c(head(sector_metrics$Index[order(-sector_metrics$Trend)], 3),
                     "Bitcoin"))
fc_names <- intersect(fc_names, names(sector_data))
plots <- lapply(fc_names, function(nm) {
  cl <- as.numeric(Cl(sector_data[[nm]])); cl <- cl[!is.na(cl)]
  fit <- tryCatch(forecast::auto.arima(tail(cl, 300)), error = function(e) NULL)
  if (is.null(fit)) fit <- forecast::ets(tail(cl, 300))
  fc <- forecast::forecast(fit, h = 30)
  hx <- tail(index(Cl(sector_data[[nm]])), 300)
  fdt <- next_bdays(max(hx), 30)
  plot_ly() |>
    add_lines(x = hx, y = tail(cl, 300), name = "History") |>
    add_lines(x = fdt, y = as.numeric(fc$mean), name = "Forecast",
              line = list(dash = "dash", color = PAL$coral_deep)) |>
    add_ribbons(x = fdt, ymin = as.numeric(fc$lower[,2]),
                ymax = as.numeric(fc$upper[,2]),
                name = "95% band", opacity = 0.2, line = list(width = 0)) |>
    pastel_layout(title = paste(nm, "— 30-session forecast (auto.arima / ets)"),
           hovermode = "x unified", showlegend = FALSE)
})
htmltools::tagList(plots)
```

Forecasting only the strongest trends (plus Bitcoin) keeps render time short; univariate models extrapolate trend and mean-reversion, which is exactly the behaviour that matters most for these flow-driven themes — and exactly why the confidence bands are wide.

# 🥇 Gold Deep Dive

Gold is the market's barometer of fear, real interest rates and currency doubt — which is why it gets its own weather station. Everything below runs on the same fallback cascade (GLD as the tradeable proxy, ~1/10 oz per share, so *levels* are ETF prices but every trend, ratio and signal is identical to spot).

```{r gold-weather, results='asis'}
#| echo: false
gm <- sector_metrics[sector_metrics$Index == "Gold (GLD)", ]
gold_story <- {
  if (gm$Trend >= 70 && isTRUE(sp_row$ROC20 < 0))
    "🥇⛈️ **Safe-haven weather.** Gold is in a strong uptrend while stocks stumble — the textbook risk-off pattern. 🐻 When gold leads and equities lag, treat every equity bounce with suspicion until breadth repairs."
  else if (gm$Trend >= 70)
    "🥇☀️ **Gold is shining on its own merits** — strong uptrend even without an equity storm. Often a real-rates or currency story. 🐻 Bear note for gold itself: parabolic phases in gold historically end with sharp 10–20% air pockets; strength is not immunity."
  else if (gm$Trend >= 50)
    "🥇🌤️ **Constructive but unhurried.** Gold trends gently higher — insurance quietly appreciating."
  else if (gm$Trend >= 35)
    "🥇⛅ **Drifting.** Gold is range-bound; the market currently sees little to hedge. That itself is information — hedges are cheapest when nobody wants them."
  else
    "🥇🌧️ **Out of favor.** Gold is in a downtrend — typically a strong-real-rates, strong-risk-appetite regime. 🐻 Ironically, gold weakness plus euphoric equities is its own late-cycle warning."
}
cat(gold_story, "\n\n")
cat(sprintf("**Gold snapshot:** Trend Score %d/100 · RSI %.0f · %+.1f%% vs 200-day MA · %+.1f%% from 52-week high · 60-day relative strength vs S&P 500: %+.1f%%.\n",
    gm$Trend, gm$RSI, (gm$Last/gm$SMA200 - 1)*100, gm$FromHigh, gm$RSvsSPX60))
```

## Price structure: candles, moving averages, Bollinger bands, support/resistance

```{r gold-candles}
#| echo: false
gx <- sector_data[["Gold (GLD)"]]
gt <- tail(gx, 250)
gcl_full <- as.numeric(Cl(gx))
bb <- tryCatch(TTR::BBands(Cl(gx), n = 20, sd = 2), error = function(e) NULL)
res_lvl <- max(as.numeric(Hi(tail(gx, 60))), na.rm = TRUE)   # 60-session resistance
sup_lvl <- min(as.numeric(Lo(tail(gx, 60))), na.rm = TRUE)   # 60-session support
idx250 <- (nrow(gx) - nrow(gt) + 1):nrow(gx)
p <- plot_ly(x = index(gt), type = "candlestick",
        open = as.numeric(Op(gt)), high = as.numeric(Hi(gt)),
        low = as.numeric(Lo(gt)), close = as.numeric(Cl(gt)), name = "Gold (GLD)") |>
  add_lines(x = index(gt), y = as.numeric(SMA(Cl(gx), 50))[idx250],
            name = "50d MA", line = list(color = PAL$butter_deep)) |>
  add_lines(x = index(gt), y = as.numeric(SMA(Cl(gx), 200))[idx250],
            name = "200d MA", line = list(color = "#b39ddb"))
if (!is.null(bb)) {
  p <- p |>
    add_lines(x = index(gt), y = as.numeric(bb[idx250, "up"]),
              name = "Bollinger up", line = list(color = "#c5cae9", dash = "dot")) |>
    add_lines(x = index(gt), y = as.numeric(bb[idx250, "dn"]),
              name = "Bollinger down", line = list(color = "#c5cae9", dash = "dot"))
}
p |> pastel_layout(title = sprintf("Gold — last 250 sessions. Support ≈ %.1f, resistance ≈ %.1f (60-session extremes)", sup_lvl, res_lvl),
            xaxis = list(rangeslider = list(visible = FALSE)),
            shapes = list(
              list(type = "line", x0 = min(index(gt)), x1 = max(index(gt)),
                   y0 = res_lvl, y1 = res_lvl, line = list(color = PAL$coral_deep, dash = "dash")),
              list(type = "line", x0 = min(index(gt)), x1 = max(index(gt)),
                   y0 = sup_lvl, y1 = sup_lvl, line = list(color = PAL$seafoam_deep, dash = "dash"))))
```

## Momentum panels: RSI and MACD

```{r gold-momentum}
#| echo: false
grsi  <- as.numeric(RSI(Cl(gx), 14))
gmacd <- tryCatch(TTR::MACD(Cl(gx)), error = function(e) NULL)
p_rsi <- plot_ly(x = index(gt), y = grsi[idx250], type = "scatter",
                 mode = "lines", name = "RSI(14)") |>
  pastel_layout(yaxis = list(title = "RSI", range = c(0, 100)),
         shapes = list(
           list(type="line", x0=min(index(gt)), x1=max(index(gt)), y0=70, y1=70,
                line=list(color=PAL$coral_deep, dash="dot")),
           list(type="line", x0=min(index(gt)), x1=max(index(gt)), y0=30, y1=30,
                line=list(color=PAL$seafoam_deep, dash="dot"))))
if (!is.null(gmacd)) {
  hist <- as.numeric(gmacd[idx250,"macd"] - gmacd[idx250,"signal"])
  p_macd <- plot_ly(x = index(gt), y = hist, type = "bar", name = "MACD hist",
                    marker = list(color = ifelse(hist >= 0, PAL$seafoam_deep, PAL$coral_deep))) |>
    add_lines(x = index(gt), y = as.numeric(gmacd[idx250,"macd"]), name = "MACD") |>
    add_lines(x = index(gt), y = as.numeric(gmacd[idx250,"signal"]), name = "Signal") |>
    pastel_layout(yaxis = list(title = "MACD"))
  subplot(p_rsi, p_macd, nrows = 2, shareX = TRUE, titleY = TRUE) |>
    pastel_layout(title = "Gold momentum: RSI(14) with 30/70 bands, MACD(12,26,9)")
} else p_rsi
```

```{r gold-momentum-text, results='asis'}
#| echo: false
r_now <- tail(grsi[!is.na(grsi)], 1)
cat(if (r_now >= 70) "📈🔥 RSI is in **overbought** territory — trends can stay overbought for a long time, but chasing entries here has poor odds. 🐻 A drop back below 70 after a stay above it is a classic short-term exhaustion signal.\n"
    else if (r_now <= 30) "🧊 RSI is **oversold** — panic territory. Historically better for patient accumulation than for capitulation, but catching knives requires gloves (position sizing).\n"
    else if (r_now >= 55) "🌤️ RSI sits in the bullish half of its range — momentum supports the trend without being stretched.\n"
    else "⛅ RSI is neutral-to-soft — momentum is not confirming a strong move in either direction.\n")
```

## Gold ratios: versus silver and versus stocks

```{r gold-ratios}
#| echo: false
slv <- sector_data[["Silver (SLV)"]]
m1 <- merge(Cl(gx), Cl(slv), join = "inner"); m1 <- m1[complete.cases(m1), ]
gs_ratio <- as.numeric(m1[,1]) / as.numeric(m1[,2])
m2 <- merge(Cl(gx), spx_cl, join = "inner"); m2 <- m2[complete.cases(m2), ]
gspx <- as.numeric(m2[,1]) / as.numeric(m2[,2]); gspx <- gspx / gspx[1] * 100
p1 <- plot_ly(x = index(m1), y = gs_ratio, type = "scatter", mode = "lines",
              name = "Gold/Silver (ETF ratio)") |>
  pastel_layout(yaxis = list(title = "GLD / SLV"))
p2 <- plot_ly(x = index(m2), y = gspx, type = "scatter", mode = "lines",
              name = "Gold vs S&P (rebased)", line = list(color = "#e6c97a")) |>
  pastel_layout(yaxis = list(title = "Gold/S&P, rebased = 100"))
subplot(p1, p2, nrows = 2, shareX = TRUE, titleY = TRUE) |>
  pastel_layout(title = "Gold/Silver ratio (ETF-based — trend identical to the oz ratio) and Gold vs S&P 500")
```

```{r gold-ratio-text, results='asis'}
#| echo: false
gsr_now <- tail(gs_ratio, 1); gsr_avg <- mean(gs_ratio)
cat(if (gsr_now > gsr_avg * 1.1) "⚖️ The gold/silver ratio is **elevated versus its own average** — gold outrunning silver is typically defensive, fear-tinged demand. 🐻 A stretched ratio plus weak equities has historically accompanied risk-off phases.\n"
    else if (gsr_now < gsr_avg * 0.9) "⚖️ The gold/silver ratio is **compressed** — silver outperforming usually signals reflation/industrial optimism rather than fear.\n"
    else "⚖️ The gold/silver ratio sits near its recent average — no strong fear or reflation message from the metals complex.\n")
grel <- tail(gspx, 1)
cat(if (grel > 105) "\n📊 Gold has been **beating the stock market** over this window — the shelter trade is winning, which is itself a quiet bear signal for equities.\n"
    else if (grel < 95) "\n📊 Stocks have been beating gold over this window — risk appetite has had the upper hand.\n"
    else "\n📊 Gold and stocks are roughly tied over this window.\n")
```

## The real-rates check (gold's gravity)

```{r gold-real-yield}
#| echo: false
real_yield <- tryCatch({
  dgs10 <- getSymbols("DGS10",  src = "FRED", auto.assign = FALSE)
  bei10 <- getSymbols("T10YIE", src = "FRED", auto.assign = FALSE)
  ry <- merge(dgs10, bei10, join = "inner"); ry <- ry[complete.cases(ry), ]
  r <- ry[,1] - ry[,2]; colnames(r) <- "RealYield10Y"
  tail(r, 500)
}, error = function(e) NULL)
if (!is.null(real_yield)) {
  plot_ly(x = index(real_yield), y = as.numeric(real_yield),
          type = "scatter", mode = "lines", name = "10Y real yield (%)") |>
    pastel_layout(title = "US 10-year real yield (FRED: DGS10 − T10YIE). Falling real yields = tailwind for gold; rising = headwind.",
           yaxis = list(title = "%"))
} else {
  cat("Real-yield data (FRED DGS10 − T10YIE) could not be fetched on this run — skipping the chart. The logic still holds: gold tends to rise when *real* (inflation-adjusted) rates fall, because the cost of holding a yieldless asset drops.")
}
```

## Gold through time & ahead

```{r gold-horizons}
#| echo: false
grow <- horizon_tbl[horizon_tbl$Asset == "Gold (GLD)", names(HORIZONS)]
gh <- data.frame(Horizon = names(HORIZONS),
                 `Return %` = round(as.numeric(unlist(grow[1, ])), 1), check.names = FALSE)
gfc <- if (!is.null(fc_all)) fc_all[fc_all$Asset == "Gold (GLD)",
        c("Horizon","Point","Chg %","Lo95","Hi95")] else NULL
htmltools::tagList(
  datatable(gh, rownames = FALSE, options = list(dom = "t"),
            caption = "Gold: realized returns by lookback window."),
  if (!is.null(gfc)) datatable(gfc, rownames = FALSE, options = list(dom = "t"),
            caption = "Gold: model projections by horizon (no 5-year forecast — see methodology). The 1-year row is directional at best.")
)
```

# 📈 Technical Trend Readings

```{r candle}
#| echo: false
nm <- "S&P 500"; x <- market[[nm]]; x <- tail(x, 180)
plot_ly(x = index(x), type = "candlestick",
        open = as.numeric(Op(x)), high = as.numeric(Hi(x)),
        low = as.numeric(Lo(x)), close = as.numeric(Cl(x)), name = nm) |>
  add_lines(x = index(x), y = as.numeric(SMA(Cl(market[[nm]]),50))[(nrow(market[[nm]])-179):nrow(market[[nm]])],
            name = "50d MA", line = list(color="orange")) |>
  pastel_layout(title = paste(nm, "— last 180 sessions with 50-day MA"),
         xaxis = list(rangeslider = list(visible = FALSE)))
```

The dashboard tables above already report RSI, MACD histogram, 20/60-day rate-of-change, distance from the 52-week high/low, and golden/death-cross detection for every index and theme via the `TTR` package.

# 💰 Valuation & Overbought Score

```{r val-table}
#| echo: false
vdf <- data.frame(
  Metric = c("Shiller CAPE (multpl.com)","Trailing P/E (multpl.com)",
             "Buffett Indicator proxy (FRED SP500/GDP)",
             "% of indices above 200d MA","Average RSI (equities)",
             "COMPOSITE HEAT SCORE"),
  Value = c(round(cape,1), round(pe,1),
            ifelse(is.na(buffett),"n/a",round(buffett,1)),
            paste0(round(pct_above200),"%"), round(avg_rsi,1),
            composite))
datatable(vdf, rownames = FALSE, options = list(dom = "t"),
          caption = "Valuation composite inputs. CAPE 35%, P/E 20%, RSI 20%, breadth 25%.")
```

The composite weights the Shiller CAPE most heavily (35%) because it is the most robust long-horizon valuation signal, then trailing P/E (20%), average RSI (20%), and breadth (25%). The Buffett Indicator is shown as a labelled proxy only, because FRED removed the Wilshire 5000 series (WILL5000PR) on June 3 2024. Note: the composite is computed on the **world index universe**, not the sector themes — that separation is deliberate, since the themes are trend-scored rather than value-scored.

# 🌡️ Sentiment, Cycle & Liquidity

```{r cycle, results='asis'}
#| echo: false
## Simple 4-phase Wyckoff-style classification on the S&P 500
sp <- metrics[metrics$Index == "S&P 500", ]
phase <- if (isTRUE(sp$AboveSMA200) && sp$ROC20 > 0) "Markup (uptrend) 🚀"
  else if (isTRUE(sp$AboveSMA200) && sp$ROC20 <= 0) "Distribution (topping) 🏔️"
  else if (!isTRUE(sp$AboveSMA200) && sp$ROC20 < 0) "Markdown (downtrend) 📉"
  else "Accumulation (basing) 🌱"
cat(sprintf("**Estimated cycle phase (S&P 500):** %s\n\n", phase))
cat(sprintf("**Fear/Greed gauge:** %d / 100.\n\n", fear_greed))
cat(sprintf("**Volatility:** VIX %.1f vs 60-day average %.1f.\n\n", vix_last, vix_avg))
```

```{r volume}
#| echo: false
#| results: asis
## Volume / low-liquidity check on S&P 500
volx <- Vo(market[["S&P 500"]])
if (!is.null(volx) && sum(as.numeric(volx), na.rm=TRUE) > 0) {
  vv <- as.numeric(volx); recent <- tail(vv,5); avg <- mean(tail(vv,60))
  cat(sprintf("Recent 5-day average volume is %.0f%% of the 60-day average — %s.",
      mean(recent)/avg*100,
      ifelse(mean(recent)/avg < 0.8, "unusually thin (low-conviction moves)","normal participation")))
}
```

Bid-ask spreads are not available on free feeds, so liquidity here is proxied by volume trends and by the VIX. The fear/greed gauge is built from three computable inputs — 20-day momentum, VIX versus its 60-day average, and the breadth of indices above their 200-day average — using only freely fetchable data.

# 🔮 Forecasts

```{r forecast}
#| echo: false
nm <- "S&P 500"; cl <- as.numeric(Cl(market[[nm]])); cl <- cl[!is.na(cl)]
fit <- tryCatch(forecast::auto.arima(tail(cl, 750)), error = function(e) NULL)
if (is.null(fit)) fit <- forecast::ets(tail(cl, 750))
fc <- forecast::forecast(fit, h = 252, level = c(80, 95))
hx <- tail(index(Cl(market[[nm]])), 750)
fdt <- next_bdays(max(hx), 252)
marks <- FC_STEPS
p <- plot_ly() |>
  add_lines(x = hx, y = tail(cl, 750), name = "History") |>
  add_ribbons(x = fdt, ymin = as.numeric(fc$lower[,2]),
              ymax = as.numeric(fc$upper[,2]),
              name = "95% band", opacity = 0.15, line = list(width = 0)) |>
  add_ribbons(x = fdt, ymin = as.numeric(fc$lower[,1]),
              ymax = as.numeric(fc$upper[,1]),
              name = "80% band", opacity = 0.25, line = list(width = 0)) |>
  add_lines(x = fdt, y = as.numeric(fc$mean), name = "Point forecast",
            line = list(dash = "dash", color = PAL$coral_deep)) |>
  add_markers(x = fdt[marks], y = as.numeric(fc$mean[marks]),
              name = "1w · 1m · 3m · 6m · 1y marks",
              marker = list(size = 9, color = "black"))
p |> pastel_layout(title = paste(nm, "— full-year fan chart with horizon marks (auto.arima). Watch the bands widen: that widening IS the forecast."),
            hovermode = "x unified")
```

```{r forecast-plain, results='asis'}
#| echo: false
## Translate the 95% bands into plain-probability sentences
lastp <- tail(cl, 1)
band_line <- function(step, label) {
  lo <- (as.numeric(fc$lower[step, 2]) / lastp - 1) * 100
  hi <- (as.numeric(fc$upper[step, 2]) / lastp - 1) * 100
  sprintf("- **%s from now** 🎲: 19 times out of 20, the model expects the S&P 500 to land somewhere between **%+.0f%%** and **%+.0f%%**.\n", label, lo, hi)
}
cat("**The same chart in plain probability language** (this is the honest version of every price target you'll ever read):\n\n")
cat(band_line(21,  "1 month"))
cat(band_line(63,  "3 months"))
cat(band_line(252, "1 year"))
cat("\nNotice how the 1-year range is wide enough to contain both a great year *and* a bad one at the same time. 🤷 That's not the model failing — that's the model being **honest**. Anyone quoting you a single confident 1-year number has simply deleted the error bars.\n")
```

```{r forecast-table}
#| echo: false
if (!is.null(fc_all)) {
  datatable(fc_all, rownames = FALSE,
            options = list(pageLength = 25, dom = "t"),
            caption = "All key-asset projections at every horizon (1 week to 1 year ahead). No 5-year forecasts — deliberately.") |>
    formatStyle("Chg %", color = styleInterval(0, c(PAL$coral_deep, PAL$seafoam_deep)))
}
```

**The reliability ladder** — how much to trust each row above:

- **1 week ahead** 🟢 — usable; mostly mean-reversion and momentum carry-over.
- **1 month ahead** 🟢 — usable; still anchored to current trend and volatility.
- **3 months ahead** 🟡 — soft; regime changes start to dominate model structure.
- **6 months ahead** 🟠 — indicative only; the 95% band typically spans an entire correction and recovery.
- **1 year ahead** 🔴 — directional at best; included because requested, trusted at your peril. 🐻 A year is long enough for the entire weather system to change twice.
- **5 years ahead** ⛔ — not produced. Univariate models at that range are astrology with confidence intervals.

Forecasts use `forecast::auto.arima()` with an `ets()` fallback — chosen over prophet to keep the document dependency-light and reproducible at any date. These are naive univariate extrapolations and must not be read as predictions.

# 📚 Methodology Appendix

- **Data cascade (reliability-first).** Every index *and every sector theme* is fetched through a chain of up to nine REAL sources, each network call retried 3x with backoff: (1–2) Yahoo v8 JSON on two independent hosts, (3) quantmod/Yahoo, (4) quantmod/Stooq, (5) direct Stooq CSV, (6) Tiingo (when an API key is configured), (7–8) a designated backup ETF for the same exposure via Yahoo and Stooq, (9) FRED official close-only series for the major indices. The winning source is recorded and shown in the dashboards. **Strict mode (default): if every real source fails for any asset, the render aborts with an error naming it — an incomplete or simulated report is never produced.** The simulated generator survives only behind `STRICT_DATA=false` for offline layout testing. Lookback is ~5.6 years so the 5-year horizon always resolves.
- **Time horizons.** Realized returns are computed over calendar windows (7/30/91/182/365/1826 days, using the last close on or before the cutoff). Forward projections read horizons off a *single* 252-step `auto.arima` forecast per key asset at 5/21/63/126/252 trading days — one fit, five readings, no re-estimation drift. **No 5-year-ahead forecast is produced**; the 1-year row is retained but explicitly labelled directional-at-best.
- **Bear Watch.** Fourteen binary warning lights (trend breaks, correction/bear thresholds, breadth < 50%, death crosses, VIX level and spike, negative momentum, near-high-but-weak-RSI divergence proxy, gold-over-stocks rotation, crypto risk-appetite drain, heat-score danger zone, yield-curve inversion, credit stress). Bear Risk Score = share of lights ON; alert text is pure if/else on that score. The executive summary always surfaces the active signals. The credit-stress light is suppressed (kept off) when either bond ETF fell back to simulated data.
- **Recession & Credit Radar.** (1) Yield curve = FRED DGS10 − DGS2, key-less; inversion (<0) trips a bear light. (2) Credit stress = HYG/LQD closing ratio through the same 5-source cascade; stress = ratio below its 200-day SMA *and* falling over 20 sessions. (3) Drawdown = close ÷ running maximum − 1, with −10%/−20% reference lines.
- **Historical odds ("What Are the Chances?").** Pure counting on the fetched S&P 500 closes: for each window length k ∈ {1, 5, 21, 63, 126, 252} trading days, the share of all k-day windows ending higher. Conditional odds split the forward-21-day return by the price-vs-200-day-SMA regime on the entry day. Overlapping windows are used (they are not independent samples — stated in the on-page footnote), and results are sample-specific to the ~5.6-year lookback.
- **Probability translations.** All 95% forecast intervals are additionally rendered as "19 times out of 20" plain-language ranges relative to the last close, so non-specialists read distributions instead of false point certainty.
- **Trend indicators (TTR):** 50/200-day SMAs, RSI(14), MACD(12,26,9) histogram, 20/60-day ROC, 52-week high/low distance, golden/death-cross detection, 50-day-MA slope.
- **Sector Trend Score (0–100):** 15 pts price>50d MA + 15 pts price>200d MA + 10 pts 50d>200d + 15 pts rising 50d MA + 15 pts scaled ROC20 + 20 pts scaled ROC60 + 10 pts proximity to 52-week high. Pure price behaviour, no valuation — deliberate for themes that trade on flows and narrative.
- **Relative strength:** 60-day change of the theme/S&P-500 price ratio.
- **Gold deep dive:** GLD candles with 50/200-day MAs and Bollinger(20,2); support/resistance = 60-session low/high extremes; RSI/MACD panels; gold/silver ETF ratio (trend-identical to the oz ratio); gold/S&P rebased ratio; US 10-year real yield from FRED (DGS10 − T10YIE, no API key needed) as gold's macro gravity; horizon returns and projections. All commentary is pre-written if/else on RSI zones, ratio-vs-average and trend score.
- **Composite heat score (0–100):** `0.35·CAPE + 0.20·P/E + 0.20·RSI + 0.25·breadth`, each sub-score min-max scaled to historical ranges; computed on world indices only.
- **Fear/greed gauge:** equal-weight blend of momentum, VIX-vs-average, and breadth.
- **Cycle phase:** simple rules on price-vs-200d MA and 20-day momentum (accumulation / markup / distribution / markdown).
- **Weather text:** pure if/else on the composite, the sector trend scores, the bear score, the gauge, VIX and breadth — the maths runs silently and only plain English with emojis is surfaced.

# ⚠️ Disclaimer

This report is generated automatically for **educational and illustrative purposes only**. It is **not financial advice**, not a recommendation to buy or sell any security or crypto-asset, and may contain errors or simulated data. Past performance and model forecasts do not guarantee future results. Consult a licensed professional before investing.
